---
title: "TrackHistoryDataAnalysis"
author: "Drew Walker"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
load("raw_music_pull_data.RData")
library(knitr)
library(tidyverse)
library(lubridate)
library(glmnet)
install.packages("summ")
library(summ)
```

#Load in Data Frame
Loads in Data frame. This is done by the last data pull done, but we can definitely change it to read in a .csv 
```{r dataload, results= "hide"}
raw_music_pull_dataframe <- totalaudio_features
```

#Data Transformation
*This creates multiple data frames that describe the music data set
**raw_music_pull_dataframe: master dataframe with all songs, the year, month, date, day, hour, last_play, recentstart, end, theoretical end of last song, new interval, and session number.
***Basically, this is ascribing "Music Listening Sessions", by identifying songs played within 1 hour (3600s).
****Can find this value in new_interval = diff > as.duration(3600).
```{r Lastfmpull, echo=TRUE, include=FALSE}
as_datetime(raw_music_pull_dataframe$date)

# ADDING SESSION VARIABLES -------------------------------------
#Convert duration_ms to millisecond period value 
milli <- dmilliseconds(raw_music_pull_dataframe$duration_ms)

#adding variables to start to create the intervals
raw_music_pull_dataframe <- raw_music_pull_dataframe %>% 
  mutate(year = year(date), 
         month = month(date), 
         day = day(date), 
         hour = hour(date),
         last_play = lead(date), 
         recentstart = as_datetime(date),
         end = (as_datetime(date) + milli),
         last_theo_end = lead(end)) %>%
  add_count(id) %>% 
  rename(song_play_count = n) %>%
  add_count(artist) %>% 
  rename(artist_play_count = n)
#make time.interval object between when the previous song could have theoretically ended and the start of the track played most recently to indicate if there was time after it finished playing or was skipped
time.interval <- raw_music_pull_dataframe$last_theo_end %--% raw_music_pull_dataframe$recentstart
#Create variable that is the difference between start time and theoretical last time played in duration
raw_music_pull_dataframe <- raw_music_pull_dataframe %>% 
  mutate(diff = as.duration(time.interval))
#REORDER
raw_music_pull_dataframe <- arrange(raw_music_pull_dataframe, date) 
#ASSIGN SESSION LABELS 
raw_music_pull_dataframe <- raw_music_pull_dataframe %>% mutate(new_interval = diff > as.duration(3600),
                      new_interval = ifelse(is.na(new_interval), FALSE, new_interval),
                      session_number = cumsum(new_interval))
```
#Summarizing session variable summaries, session lengths, session midpoints 
*Creates session_summary data frame, which is a dataframe where rows are different music listening sessions in this data set. We summarise the session valence, energy, key, loudness, sessionmonth, lastsongdate time and first songdatetimer
```{r session summaries}
#Summarizing session variable summaries, session lengths, session midpoints 
by_session_number <- group_by(raw_music_pull_dataframe, session_number)
session_summary <- summarise(by_session_number,
                   count = n(),
                   session_valence_mean = mean(valence, na.rm = TRUE),
                   session_energy_mean = mean(energy, na.rm = TRUE),
                   session_key_mean = mean(key, na.rm = TRUE),
                   session_loudness_mean = mean(loudness, na.rm = TRUE),
                   sessionmonth = mean(month, na.rm = TRUE),
                   lastsongdatetime = max(end, na.rm = TRUE),
                   firstsongdatetime = min(recentstart, na.rm = TRUE))
#Making session length duration objects
sessionlength <- session_summary$firstsongdatetime %--% session_summary$lastsongdatetime
midpointinterval <- sessionlength/2
#Adding session duration, midpointdatetime variables
session_summary <- session_summary %>% 
  mutate(midpointdatetime = firstsongdatetime + as.duration(midpointinterval),
         duration = as.duration(sessionlength))
```
```{r, dailysummaries}
#Creating daily summary dataframe to group by date and days of week
dailysummaries <- raw_music_pull_dataframe %>% 
  mutate(justdate = ymd(as.Date(date)),
         dayofweek = wday(as.Date(date),label = TRUE, abbr = FALSE))
#Grouping by justdate
dailysummaries_justdate <- dailysummaries %>% 
  group_by(justdate) %>% 
  summarise(dailyvalence_mean = mean(valence, na.rm =TRUE),
            dailydanceability_mean = mean(danceability, na.rm =TRUE)) %>% 
  mutate(dayofweek = wday(as.Date(justdate),label = TRUE, abbr = FALSE))

#Grouping by days of the week-- this one returns NAs for valence for some reason
dailysummaries_weekdays <- dailysummaries_justdate %>% 
  group_by(dayofweek) %>% 
    summarise(weekdayvalence_mean = mean(dailyvalence_mean, na.rm = TRUE),
              weekdaydanceability_mean = mean(dailydanceability_mean, na.rm = TRUE))
```

```{r valence,justdates, weekdays}
valence_by_justdates <- ggplot(dailysummaries_justdate, aes(x = justdate, y = dailyvalence_mean)) +
  labs(x = "Date", y = "Valence")+
  geom_point(mapping = aes(color = dayofweek)) + 
  geom_smooth()
valence_by_justdates

valence_by_dayofweek <- ggplot(dailysummaries_weekdays, aes(x = dayofweek, y = weekdayvalence_mean, fill = dayofweek, label = dayofweek))+
  geom_col(show.legend = TRUE)+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Mean Valence by Day of Week"))
valence_by_dayofweek
```

```{r danceability,justdates, weekdays}
danceability_by_justdates <- ggplot(dailysummaries_justdate, aes(x = justdate, y = dailydanceability_mean)) +
  labs(x = "Date", y = "Danceability")+
  geom_point(mapping = aes(color = dayofweek)) + 
  geom_smooth()
danceability_by_justdates

danceability_by_dayofweek <- ggplot(dailysummaries_weekdays, aes(x = dayofweek, y = weekdaydanceability_mean, fill = dayofweek, label = dayofweek))+
  geom_col(show.legend = TRUE)+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Mean Danceability by Day of Week"))
danceability_by_dayofweek
```


##Most Popular Artists and Songs
```{r, song_and_artist_popularity, include=TRUE}
top25artists <- raw_music_pull_dataframe %>% 
  group_by(artist) %>% 
  summarize(
  across(where(is.numeric), mean)) %>% 
  slice_max(artist_play_count, n = 25)

p_top25artists_play_count <- ggplot(data = top25artists, aes(reorder(artist, artist_play_count), y = artist_play_count, fill = artist, label = artist_play_count))+
  geom_col(show.legend = TRUE)+
  geom_text(aes(label = artist_play_count))+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Your Top Played Artists by Number of Plays"))+
  coord_flip()
p_top25artists_play_count
ggsave("top25artists.png")


#For some reason, this seems to be less accurate than artist values
top25songs <- raw_music_pull_dataframe %>% 
  slice_max(song_play_count, n = 25, with_ties = FALSE)

p_top25songs_play_count <- ggplot(data = top25songs, aes(reorder(title, song_play_count), y = song_play_count, fill = title, label = song_play_count))+
  geom_col(show.legend = FALSE)+
  geom_text(aes(label = song_play_count))+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Your Top Played Songs by Number of Plays"))+
  coord_flip()
p_top25songs_play_count
ggsave("top25songs.png")
```

#Visualizations
Next, we need to do visualizations (interactive) of these dataframes.
*Need to find ways to repel the labels of these visualizations (with the repeller package)
*May look back on the tidytuesday posts for the spotify data
*Ways to identify tops of certain categories
*Ways to identify most popular songs in different categories (Favorite upbeat song, favorite sad song) 


```{r, modeling}
#EDA
numbas <- raw_music_pull_dataframe %>% 
  select(where(is.numeric)) %>% 
  rename(music_key = key)

histograms <- ggplot(gather(numbas), aes(value)) + 
    geom_histogram(bins = 10) + 
    facet_wrap(~key, scales = 'free_x')
ggsave("histies.png", plot = histograms)
library(sandwich)
library(msm)
#Primary model for song_play_count Outcome

m1 <- glm(song_play_count ~ valence + danceability, family="poisson", data= numbas)
#Confidence intervals 
cov.m1 <- vcovHC(m1, type="HC0")
std.err <- sqrt(diag(cov.m1))
r.est <- cbind(Estimate= coef(m1), "Robust SE" = std.err,
"Pr(>|z|)" = 2 * pnorm(abs(coef(m1)/std.err), lower.tail=FALSE),
LL = coef(m1) - 1.96 * std.err,
UL = coef(m1) + 1.96 * std.err)

r.est

#other models 
valence_and_playcount <- summary(m1 <- glm(song_play_count ~ valence + danceability, family="poisson", data= numbas))

liveness_on_song_play_count <- summary(m1 <- glm(song_play_count ~ loudness, family="poisson", data= numbas))
liveness_on_song_play_count

#categorical 
fitty <- lm(valence ~ year, data =raw_music_pull_dataframe)
fitty
artist_playcount_and_playcount
```


