---
title: "TrackHistoryPull"
author: "Drew Walker"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
library(tidyverse)
library(devtools)
library(spotifyr)
library(scrobbler)
library(purrr)
library(dplyr)
library(Rcpp)
library(knitr)
library(lubridate)
library(furrr)
library(tictoc)
```

## Creating Functions
Creates function to search through spotify by artist, title, and return the first track on the list. Creates failsafe to produce a tibble() if it doesn't work.
```{r tracksearch function}
track_audio_features <- function(artist, title, type = "track") {
  search_results <- search_spotify(paste(artist, title), type = type)
  track_audio_feats <- get_track_audio_features(search_results$id[[1]])
  return(track_audio_feats)
}
# create a version of this function which can handle errors
possible_af <- possibly(track_audio_features, otherwise = tibble())
```

## Last.fm pull
*Change USER for filenaming to your Last.fm account name 
* download_scrobbles(username = "USER")
```{r Lastfmpull, echo=FALSE}
my_data <- scrobbler::download_scrobbles(username = "thedrewwalker", api_key = "50d7685d484772f2ff42c45891b31c7b")
```


#This sets up system env variables that grant our app authorization to pull GET requests from Spotify API
```{r systemenvironments}
Sys.setenv(SPOTIFY_CLIENT_ID = '2c46a5d6764f425ab746a56a1c8791b9')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '9b809cd5be004e8fbbc72ad74b0e19a7')
access_token <- get_spotify_access_token(client_id = Sys.getenv("SPOTIFY_CLIENT_ID"), 
                                         client_secret = Sys.getenv("SPOTIFY_CLIENT_SECRET"))
#prepare last.fm df for merge
colnames(my_data)
colnames(my_data)[colnames(my_data)=="song_title"] <- "title"
```

Now, we'll make a function that applys the search track audio features through the rows of artists and track titles.

# Mapping search function -------------------------------------------------
```{r mappingsearchfunction}
tic()
future::plan(multiprocess)
possible_feats <- possibly(track_audio_features, otherwise = tibble("NA"))
totalaudio_features <- my_data %>%
  mutate(audio_features = future_map2(artist, title, possible_feats)) %>%
  unnest() %>% 
  as_tibble()
toc()
```
The following code will create one huge .csv file
We will also change the dates given by last.fm to UTC timestamps, EST to match clinical study data. *It's worth noting we are only accurate to the minute
```{r timezoneadjust}
totalaudio_features$date <- dmy_hm(totalaudio_features$date)
#Now we'll convert to change to US Timezone for easier data analysis
totalaudio_features$date <- with_tz(totalaudio_features$date, tzone = "US/Eastern")
#Then we make a title element that updates with the timestamp of the data pull. MAKE SURE YOU CHANGE USER HERE
```
#Create .csv of music history data
*CHANGE USER FOR FILENAMING 
```{r filecreation}
csvFileName <- paste("User",format(Sys.time(),"%d-%b-%Y %H.%M"),".csv")
#and we make the csv that will be saved in the working directory 
write.csv(totalaudio_features, file = csvFileName)
#©Copyright September 12th, 2019, University of Florida Research Foundation, Inc. All Rights Reserved.
```
#TheData
```{r showdata}
totalaudio_features
```
```{r, save_data_for_transformation}
save.image(file = "raw_music_pull_data.RData")

```



